manuscript

### 2022-09-23 ms/manuscript.Rmd
update ms

Generalist parasites, such as ranaviruses, are commonly found in nature and often use a range of alternative host species to reproduce (Park et al., 2018; Poulin et al., 2011). The transmission potential of a generalist parasite for a given host species may vary due to differences in host species abundances (Fenton et al., 2002; Hopkins et al., 2020), host competence (i.e. the ability for an individual host to become infected and pass infection on to others (Martin et al., 2019)), and the environmental conditions in which the interaction takes place (Altizer et al., 2013; Cable et al., 2017; Rohr et al., 2011). The combination of these factors makes it difficult to assess how multi-species host communities are differentially at risk of parasite invasion and onward transmission to other communities (P T J Johnson et al., 2015). One method to separately quantify the effects of host abundance and competence on parasite transmission is to use community competence: the weighted average of competence values of host species in the community (Pieter T.J. Johnson et al., 2013a). In addition, community competence is advantageous because it considers the relative abundance of a species rather than the presence of a species alone. For example, a commonly occurring, low-competence host could be responsible for more transmission than a rare, high-competence host (Holt et al., 2003). In contrast to host species richness, which is the typical predictor variable in the dilution effect hypothesis literature, community competence and host abundance are more directly related to the parasite basic reproductive number, R0 (Dobson, 2004; Rohr et al., 2019).

>>>>

Generalist parasites, such as ranaviruses, are commonly found in nature and often use a range of alternative host species to reproduce [@park_characterizing_2018; @poulin_comparative_2011]. The transmission potential of a generalist parasite for a given host species may vary due to differences in host species abundances [@fenton_parasite_2002; @hopkins_systematic_2020], host competence (i.e. the ability for an individual host to become infected and pass infection on to others [@martin_burrows_2019]), and the environmental conditions in which the interaction takes place [@altizer_climate_2013; @cable_global_2017; @rohr_frontiers_2011]. The combination of these factors makes it difficult to assess how multi-species host communities are differentially at risk of parasite invasion and onward transmission to other communities [@johnson_why_2015]. One method to separately quantify the effects of host abundance and competence on parasite transmission is to use community competence: the weighted average of competence values of host species in the community [@johnson_biodiversity_2013]. In addition, community competence is advantageous because it considers the relative abundance of a species rather than the presence of a species alone. For example, a commonly occurring, low-competence host could be responsible for more transmission than a rare, high-competence host [@holt_parasite_2003]. In contrast to host species richness, which is the typical predictor variable in the dilution effect hypothesis literature, community competence and host abundance are more directly related to the parasite basic reproductive number, R0 [@dobson_population_2004; @rohr_towards_2019].
